Stats Project 2

### 2022-12-12 article.Rmd
add plots to article

@@

@@

@@

-   Excessively Expensive \> 700k SalePrice: ID #692 & \# 1183 -

@@

>>>>

```{r}

a1_set %>% ggplot(aes(x = (GrLivArea), y = SalePrice/1000, color = Neighborhood)) + geom_point() + stat_smooth(method = "lm")

a1_set %>% ggplot(aes(x = SalePrice/10000, fill = Neighborhood)) + geom_histogram(bins =20)

a1_set %>% ggplot(aes(x = GrLivArea, fill = Neighborhood)) + geom_histogram(bins =20)
```

@@

#put the plots here
plot(fit_transform)
```

@@

```{r}
plot(t1fit)
```

@@

-   Excessively Expensive \> 700k SalePrice: ID #692 & \# 1183

@@

Stepwise Selection

Regression model:

Mean(SalePrice) = b0 + b1(OverallQual) + b2(OverallCond) + b3(YearBuilt) + b4(
